A Note on Convergence Diagnostics for Multiple Imputation using Chained Equations (MICE)

### 2019-11-19 Simulation/Writeup/NoteConvergence.Rnw
Feedback Research Seminar

>>>>

Feedback research seminar: order is not intuitive, mentioned, explained later. short sentences with a lot of content. implicitly a lot happens. expand sentence or it's obvious and i should delete it. Explain 'true data generating model'. follow important concepts with explanation or examples in next part. Look at abbreviations. for example r hat is just metnioned as 'e.g.' not clear in intro how important it is. also, look at distinction between mi and mice, they look like synonyms now. look at imputing vs analysing because they're called steps somewhere, and something else somewhere else. explain what a chain is. make clear when i talk about my study or lit. look at equations vehtari, because there is no real need for it. try to rephrase in my own words because of text flow. make clear that i only generate 1 dataset (not simulated data). in figure, r hat looks stable after 20 it. in discussion, explain that less it is advantage of mi, not a disadv. compared to MCMC. then final par is too negative, explain scope in intro instead.
